COVID-19 and Online Learning Tools

### 2021-12-26 Paper_online_Learning.Rmd
update keywords

---
title: "Attention Towards Distance Education Tools During COVID-19 Pandemic: Evidence from Google Trends"
author:
- familyname: Talagala 
  othernames: Priyanga Dilini
  address: Department of Compuational Mathematics, University of Moratuwa, Sri Lanka
  email: priyangad@uom.lk
  correspondingauthor: true
- familyname: Talagala
  othernames: Thiyanga S.
  address: Department of Statistics, Faculty of Applied Sciences, University of Sri Jayewardenepura, Sri Lanka
  email: ttalagala@sjp.ac.lk
abstract: "Distance Education has a long history. However COVID-19 has made a new era of distance education. With the increasing demand various distance learning solutions have been introduced for different education purposes. In this study we invetigated the impact of COVID-19 on ditance education and the possibility of using Google Trend search queries as a proxy to quantify the  popularity and the public interest towards different distance education solutions. Both visual and analytical approaches were used to  analyse global level web search querie during COVID-19 pandemic. The findings of this study include a Google Trend footprint of various distance leraning solutions that can be used as a proxy for measuring global attention towards different distance learning solutions. The can provide a fast first step guide to identify the most popular distance learning tools available for different educational purposes. R code and data to reproduce the results of this work are available in the online supplementary materials."
keywords:  "Online-learning, Distance education solutions, COVID-19 Pandemic,  Google Trend search queries "
wpnumber: 1
jelcodes: C82,I20,I21
blind: false
cover: true
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
output:
  templatehub::workingpaper:
    fig_caption: yes
    fig_height: 10
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

>>>>

---
title: "COVID-19 and Online Learning Tools"
author:
- familyname: Talagala 
  othernames: Priyanga Dilini
  address: Department of Compuational Mathematics, University of Moratuwa, Sri Lanka
  email: priyangad@uom.lk
  correspondingauthor: true
- familyname: Talagala
  othernames: Thiyanga S.
  address: Department of Statistics, Faculty of Applied Sciences, University of Sri Jayewardenepura, Sri Lanka
  email: ttalagala@sjp.ac.lk
abstract: "Distance Education has a long history. However COVID-19 has made a new era of distance education. With the increasing demand various distance learning solutions have been introduced for different education purposes. In this study we invetigated the impact of COVID-19 on ditance education and the possibility of using Google Trend search queries as a proxy to quantify the  popularity and the public interest towards different distance education solutions. Both visual and analytical approaches were used to  analyse global level web search querie during COVID-19 pandemic. The findings of this study include a Google Trend footprint of various distance leraning solutions that can be used as a proxy for measuring global attention towards different distance learning solutions. The can provide a fast first step guide to identify the most popular distance learning tools available for different educational purposes. R code and data to reproduce the results of this work are available in the online supplementary materials."
keywords:  "Online-learning, Distance education solutions, COVID-19 Pandemic,  Google Trend search queries, Online-teaching "
wpnumber: 1
jelcodes: C82,I20,I21
blind: false
cover: true
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
output:
  templatehub::workingpaper:
    fig_caption: yes
    fig_height: 10
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

### 2021-12-26 Paper_online_Learning.tex
update keywords

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Attention Towards Distance Education Tools During COVID-19 Pandemic: Evidence from Google Trends},
            pdfkeywords={Online-learning, Distance education solutions, COVID-19 Pandemic, Google Trend search queries},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\usepackage[style=authoryear-comp,]{biblatex}
\addbibresource{references.bib}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\title{Attention Towards Distance Education Tools During COVID-19 Pandemic: Evidence from Google Trends}

@@

\begin{document}
\maketitle
\begin{abstract}
Distance Education has a long history. However COVID-19 has made a new era of distance education. With the increasing demand various distance learning solutions have been introduced for different education purposes. In this study we invetigated the impact of COVID-19 on ditance education and the possibility of using Google Trend search queries as a proxy to quantify the popularity and the public interest towards different distance education solutions. Both visual and analytical approaches were used to analyse global level web search querie during COVID-19 pandemic. The findings of this study include a Google Trend footprint of various distance leraning solutions that can be used as a proxy for measuring global attention towards different distance learning solutions. The can provide a fast first step guide to identify the most popular distance learning tools available for different educational purposes. R code and data to reproduce the results of this work are available in the online supplementary materials.
\end{abstract}
\begin{keywords}
Online-learning, Distance education solutions, COVID-19 Pandemic, Google Trend search queries
\end{keywords}

>>>>

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={COVID-19 and Online Learning Tools},
            pdfkeywords={Online-learning, Distance education solutions, COVID-19 Pandemic, Google Trend search queries, Online-teaching},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\usepackage[style=authoryear-comp,]{biblatex}
\addbibresource{references.bib}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\title{COVID-19 and Online Learning Tools}

@@

\begin{document}
\maketitle
\begin{abstract}
Distance Education has a long history. However COVID-19 has made a new era of distance education. With the increasing demand various distance learning solutions have been introduced for different education purposes. In this study we invetigated the impact of COVID-19 on ditance education and the possibility of using Google Trend search queries as a proxy to quantify the popularity and the public interest towards different distance education solutions. Both visual and analytical approaches were used to analyse global level web search querie during COVID-19 pandemic. The findings of this study include a Google Trend footprint of various distance leraning solutions that can be used as a proxy for measuring global attention towards different distance learning solutions. The can provide a fast first step guide to identify the most popular distance learning tools available for different educational purposes. R code and data to reproduce the results of this work are available in the online supplementary materials.
\end{abstract}
\begin{keywords}
Online-learning, Distance education solutions, COVID-19 Pandemic, Google Trend search queries, Online-teaching
\end{keywords}
